Towards human SuperEEG

### 2018-10-07 paper/main.tex
results section, density results [WIP]

@@

We also wondered whether reconstruction quality (measured as the
correlation between the observed and reconstructed data) varied with
the electrode locations (Fig.~\ref{fig:corrmap}B \& D). In general, reconstruction quality remained high throughout the brain. Although reconstruction accuracy appeared high in the medial temporal lobe, which is a common epileptic focus (and therefore a common target for electrode implantation), we observed a weak but statistically reliable negative correlation between reconstruction quality and electrode density (defined as the proportion of electrodes within 20 MNI units for each location; dataset 1: $r = -0.07, p < 10^{-5}$, dataset 2: $r = -0.16, p < 10^{-10}$). This provides some evidence that our reconstruction accuracy results cannot be driven only by volume conductance.  Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions. Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A, B); $r = 0.57, p < 10^{-10}$).

>>>>

Although both datasets we examined provide good full-brain coverage
(when considering data from every patient; e.g.\
Fig.~\ref{fig:corrmap}B, D), electrodes are not placed uniformly
throughout the brain.  For example, electrodes are more likely to be
implanted in regions like the medial temporal lobe (MTL), and are
rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
Separately for each dataset, for each voxel in the XXX~mm$^3$ voxel
MNI152 brain, we computed the proportion of electrodes contained
within a 20 MNI unit radius sphere centered on that voxel.  We defined
the \textit{density} at that location as this proportion.  Across
Datasets 1 and 2, the electrode placement densities were similar
(correlation by voxel: $r = 0.57, p < 10^{-10}$).  We wondered whether
regions with good covererage might be associated with better
reconstruction accuracy (e.g. Fig.~\ref{fig:corrmap}B, D indicate that
many electrodes in the MTL have relatively high reconstruction
accuracy, and occiptal electrodes tend to have relatively low
reconstruction accuracy).  To test whether this held more generally
across the entire brain, for each dataset we computed the electrode
placement density for each electrode from each patient (using the
proportion of \textit{other} patients' electrodes within 20 MNI units
of the given electrode).  We then correlated these density values with
the across-patient reconstruction accuracies for each electrode.
Contrary to our expectation, rather than positive correlations, we
found weak (but reliable) negative correlations between reconstruction
accuracy and density for both datasets (Dataset 1: $r = XXX, p = XXX$;
Dataset 2: $r = -0.16, p < 10^{-10}$).  This indicates that the
reconstruction accuracies we observed are not driven solely by
sampling density, but rather may also reflect higher order properties
of neural dynamics such as functional correlations between distant
voxels~\citep{BetzEtal17b}.

@@
